Reanalysis Step 2: Multiple Imputation

### 2025-08-30 reanalysis-2-multiple_imputation.qmd
simplify

>>>>

## Post-Imputation Completeness

```{r post-imputation-completeness}
# Table of variables with remaining missingness in the first completed dataset
comp_table <- tibble(
  Variable = names(first_imp),
  Present = colSums(!is.na(first_imp)),
  Missing = colSums(is.na(first_imp))
) |>
  dplyr::mutate(MissingPct = round(Missing / nrow(first_imp) * 100, 2)) |>
  dplyr::arrange(dplyr::desc(Missing))

vars_with_missing <- comp_table |>
  dplyr::filter(Missing > 0)

if (nrow(vars_with_missing) > 0) {
  kable(vars_with_missing, caption = "Variables with missing data after imputation (first completed dataset)")
} else {
  kable(tibble(Message = "No variables with missing data after imputation (first completed dataset)"))
}
```
